### 2021-05-09 docs/manuscript/PLOS-MSc-Thesis.tex
Implement highlighting of changes

@@

Cells interact continuously with their environment and they must detect signals
from it. In many cases Gene Regulatory Networks (GRNs) interpret these signals
through gene interaction and produce a particular response. This information
processing function is of particular importance in developmental processes such
as those in which a group of cells differentiate in response to a signalling
molecule. Such molecules were referred to as morphogens by Turing in 1952
\cite{Turing1952} and posterior theoretical studies on patterning led to the
conceptualization of the French Flag Problem by Wolpert, who also stated
in this respect that a gradient of concentration of a morphogen could
trigger cell differentiation in a one-dimensional field of cells
\cite{Wolpert1969, sharpe_2019}.
Although the Bicoid protein (bcd), the first example of a molecule that acted
as a morphogen, was only found in the 80's in the developing embryos of
\textit{Drosophila melanogaster}
\cite{driever_gradient_1988, driever_bicoid_1988}, now it is known that there
are many other examples such as the Decapentaplegic (Dpp) protein in
\textit{Drosophila} wing imaginal discs \cite{affolter_decapentaplegic_2007},
as well as Sonic Hedgehog \cite{dessaud_dynamic_2010,cohen_theoretical_2014}
and Wnt \cite{raspopovic_digit_2014}. However, information processing by GRNs
has proven to be a complex process, and a major goal of developmental biology
is to understand mechanistically how positional information given by morphogens
is translated in spatial differentiation.\\

@@

Cotterell and Sharpe studied what kind of 3-node network topologies could
interact with a morphogen gradient and produce a stripe of gene expression
in a one-dimensional field of cells and found a variety of networks that
implemented at least 7 different mechanisms and had different levels of
complexity \cite{Cotterell2010}.

@@

The degree distribution of this network seems to follow a Poisson distribution
(Pearson’s $\chi^2 = 12.8902$, $\text{p-value} = 0.115684$) characteristic of a
Erdös-Rényi network \cite{Erdos1959}. This kind of network presents a great
number of nodes with low degree and a few nodes with high degree
(Fig~\ref{fig:deg-dist}A). Nodes corresponding to topologies number one and
three showed the highest degree ($deg(1) = deg (3) = 14$). Curiously, nodes with
higher degree resulted to be also those network topologies with higher abundance
(Fig~\ref{fig:deg-dist}B). This relationship between abundance and node degree
was corroborated by the Spearman's rank correlation coefficient
($r_S = 0.353752$, $p = 6.2933\times10^{-23} $).

>>>>

% Highlight changes
\usepackage{color,soul}
\newcommand{\hil}[1]{\hl{#1}} % Highlight changes
% \newcommand{\hil}[1]{#1} % Do nothing, clean version

@@

Cells interact continuously with their environment and they must detect signals
from it. In many cases Gene Regulatory Networks (GRNs) interpret these signals
through gene interaction and produce a particular response. This information
processing function is of particular importance in developmental processes such
as those in which a group of cells differentiate in response to a signalling
molecule. Such molecules were referred to as morphogens by Turing in 1952
\cite{Turing1952} \hil{and posterior theoretical studies on patterning led to the
conceptualization of the French Flag Problem by Wolpert, who also stated
in this respect that a gradient of concentration of a morphogen could
trigger cell differentiation in a one-dimensional field of cells}
\cite{Wolpert1969, sharpe_2019}.
Although the Bicoid protein (bcd), the first example of a molecule that acted
as a morphogen, was only found in the 80's in the developing embryos of
\textit{Drosophila melanogaster}
\cite{driever_gradient_1988, driever_bicoid_1988}, now it is known that there
are many other examples such as the Decapentaplegic (Dpp) protein in
\textit{Drosophila} wing imaginal discs \cite{affolter_decapentaplegic_2007},
as well as Sonic Hedgehog \cite{dessaud_dynamic_2010,cohen_theoretical_2014}
and Wnt \cite{raspopovic_digit_2014}. However, information processing by GRNs
has proven to be a complex process, and a major goal of developmental biology
is to understand mechanistically how positional information given by morphogens
is translated in spatial differentiation.\\

@@

\hil{Cotterell and Sharpe studied what kind of 3-node network topologies could
interact with a morphogen gradient and produce a stripe of gene expression
in a one-dimensional field of cells and found a variety of networks that
implemented at least 7 different mechanisms and had different levels of
complexity} \cite{Cotterell2010}.

@@

The degree distribution of this network seems to follow a Poisson distribution
(Pearson’s $\chi^2 = 12.8902$, $\text{p-value} = 0.115684$) characteristic of a
Erdös-Rényi network \cite{Erdos1959}. This kind of network presents a great
number of nodes with low degree and a few nodes with high degree
(Fig~\ref{fig:deg-dist}A). Nodes corresponding to topologies number one and
three showed the highest degree ($deg(1) = deg (3) = 14$). Curiously, nodes with
higher degree resulted to be also those network topologies with higher abundance
(Fig~\ref{fig:deg-dist}B). This relationship between abundance and node degree
was corroborated by the Spearman's rank correlation coefficient
(\hil{$r_S = 0.353752$}, $p = 6.2933\times10^{-23} $).
